\chapter{Acknowledgements}

First and foremost, I would like to express my sincere thanks and gratitude to
my project supervisors Dr Vince Knight and Henry Wilde for their continual
advice, support and invaluable ideas throughout the completion of this project.
You have always been willing to lend a hand or provide encouragement when
it was needed the most. I do not think I could have gotten better supervisors
and I apologise for not achieving everything in the plan. You have assisted me
through what will probably be the largest project I will ever do!

There are many people who have helped and supported me, both inside and outside
university, over the past four years of my undergraduate degree here at Cardiff
School of Mathematics. If I was to mention all the names, this would be longer
than my whole project! Therefore, this `thank you' is for all those who I have
had the pleasure of being taught by and working with during my degree. You have
made this journey an interesting and enjoyable one and I will continue to be
inspired by the passion all the lecturers have for what they do. 

Also, I would like to give special mention to Nikoleta, who, even though is in
her final few months of a PhD (probably the most challenging period), found time
to have chats with me and make sure I was still operating on this planet. You
encouraged me and always had a positive thing to say when I was convinced
everything was going to end terribly. So thank you very much Nikoleta, for being
such a great friend and best of luck with the completion of your thesis!

Last but most certainly not least, I want to say a huge thank you to my Mum, Dad
and Zoe for their continual love and support. To say these have been a
challenging four years is an understatement but you were always there for me
through it all. If it was not for your belief that I could achieve it I do not
think I could have completed this project, let alone the past four years! My
Mum, thank you for keeping me fuelled with coffee and biscuits through the long
days and for being a shoulder to cry on when necessary (I will pay you back with
hair dye, for all those grey ones I caused!). Dad, thank you for making me laugh
(and cry) with your terrible jokes and I promise I will replace all those grains
of coffee I had from `your' coffee pot. Finally, my sister Zoe (yes, you are
getting a mention because, yes, you did play a key part) thank you for keeping
me sane and always making me smile.

To all those who I have forgotten to mention: my sincerest apologies and thank
you for all your support.